### 2022-04-27 manuscript.tex
mario [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/42d00d9da7916e425b089dedafe60ffe6cc10173.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/42d00d9da7916e425b089dedafe60ffe6cc10173/checks
https://github.com/scherzerthesis/thesis/actions/runs/2234500322

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/eaf13b4469216af1bafbda0b8626cd110d0b56cf/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/eaf13b4469216af1bafbda0b8626cd110d0b56cf}{scherzerthesis/thesis@eaf13b4}
on April 10, 2022.

@@

\textbf{Genetically engineered mouse models} Genetically-Engineered mouse models (GEMMs) of human cancer have allowed for the reproducible analysis of cancer biology driven by specific mutations frequently found in cancer patients. These models are helpful in understanding the molecular mechanisms that drive tumor formation and testing tumor responses to targeted or immune therapies. Early mouse models were not engineered but instead selected inbred mouse strains that were natural hosts of tumor transplantation(Strong, 1978). However, these models suffer from long latencies, incomplete penetrance, and are often not genetically similar to human cancers. Therefore, carcinogen-induced models such as UV, Urethane, radiation, cigarette consumption, or MNU treatment models were developed to resemble carcinogen-induced human cancers(Kemp et al., 1994; Westcott et al., 2014). After techniques were developed to genetically manipulate embryonic stem cells came the ability to engineer mice with specific mutations that could drive tumor formation. Since genes involved in cancer are also crucial for normal mouse development, conditional gene manipulation was developed to allow for temporal control.

@@

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/42d00d9da7916e425b089dedafe60ffe6cc10173/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/42d00d9da7916e425b089dedafe60ffe6cc10173}{scherzerthesis/thesis@42d00d9}
on April 27, 2022.

@@

\textbf{Genetically engineered mouse models} Genetically-Engineered mouse models (GEMMs) of human cancer have allowed for the reproducible analysis of cancer biology driven by specific mutations frequently found in cancer patients. These models are helpful in understanding the molecular mechanisms that drive tumor formation and testing tumor responses to targeted or immune therapies. Early mouse models were not engineered but instead selected inbred mouse strains that were natural hosts of tumor transplantation(Strong, 1978). However, these models suffer from long latencies, incomplete penetrance, and are often not genetically similar to human cancers. Therefore, carcinogen-induced models such as UV, Urethane, radiation, cigarette consumption, or MNU treatment models were developed to resemble carcinogen-induced human cancers(Kemp et al., 1994; Westcott et al., 2014). After techniques were developed to genetically manipulate embryonic stem cells using the came the ability to engineer mice with specific mutations that could drive tumor formation(Thomas et al., 1986). Since genes involved in cancer are also crucial for normal mouse development, conditional gene manipulation was developed to allow for temporal control.

@@

\leavevmode\vadjust pre{\hypertarget{ref-DB0qT9Ty}{}}%
Thomas, K.R., Folger, K.R., and Capecchi, M.R. (1986). High frequency targeting of genes to specific sites in the mammalian genome. Cell \emph{44}, 419--428. \url{https://doi.org/10.1016/0092-8674(86)90463-0}.
